% **************************************************************************************************************
% A Classic Thesis Style
% An Homage to The Elements of Typographic Style
%
% Copyright (C) 2015 André Miede http://www.miede.de
%
% If you like the style then I would appreciate a postcard. My address 
% can be found in the file ClassicThesis.pdf. A collection of the 
% postcards I received so far is available online at 
% http://postcards.miede.de
%
% License:
% This program is free software; you can redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation; either version 2 of the License, or
% (at your option) any later version.
%
% This program is distributed in the hope that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with this program; see the file COPYING.  If not, write to
% the Free Software Foundation, Inc., 59 Temple Place - Suite 330,
% Boston, MA 02111-1307, USA.
%
% **************************************************************************************************************
\RequirePackage{fix-cm} % fix some latex issues see: http://texdoc.net/texmf-dist/doc/latex/base/fixltx2e.pdf
\documentclass[ twoside,openright,titlepage,numbers=noenddot,headinclude,%1headlines,% letterpaper a4paper
                footinclude=true,cleardoublepage=empty,abstractoff, % <--- obsolete, remove (todo)
                BCOR=5mm,paper=a4,fontsize=11pt,%11pt,a4paper,%
                ngerman,american,%
                ]{scrreprt}

%********************************************************************
% Note: Make all your adjustments in here
%*******************************************************
\input{classicthesis-config}

%********************************************************************
% Bibliographies
%*******************************************************
\addbibresource{Bibliography.bib}
\addbibresource[label=ownpubs]{AMiede_Publications.bib}

%********************************************************************
% Hyphenation
%*******************************************************
%\hyphenation{put special hyphenation here}

% ********************************************************************
% GO!GO!GO! MOVE IT!
%*******************************************************
\begin{document}
\frenchspacing
\raggedbottom
\selectlanguage{american} % american ngerman
%\renewcommand*{\bibname}{new name}
%\setbibpreamble{}
\pagenumbering{roman}
\pagestyle{plain}
%********************************************************************
% Frontmatter
%*******************************************************
\include{FrontBackmatter/DirtyTitlepage}
\include{FrontBackmatter/Titlepage}
\include{FrontBackmatter/Titleback}
\cleardoublepage\include{FrontBackmatter/Dedication}
%\cleardoublepage\include{FrontBackmatter/Foreword}
\cleardoublepage\include{FrontBackmatter/Abstract}
%\cleardoublepage\include{FrontBackmatter/Publications}
%\cleardoublepage\include{FrontBackmatter/Acknowledgments}
\pagestyle{scrheadings}
\cleardoublepage\include{FrontBackmatter/Contents}
%********************************************************************
% Mainmatter
%*******************************************************
\cleardoublepage\pagenumbering{arabic}
%\setcounter{page}{90}
% use \cleardoublepage here to avoid problems with pdfbookmark
\cleardoublepage
% What should a thesis contain:

\ctparttext{The following reflects what I believe to be a good structure
  for a report or a thesis in experimental computer science. 
It contains a natural progression from the general to the specific, and
from the work of others to the work by the authors, each chapter
forming the foundation of the next.}
\part{The Proper Structure of a Thesis}
\label{part:prop-struct-thes}
\cleardoublepage

\include{Chapters/introduction}
\include{Chapters/relatedwork}
\include{Chapters/analysis}
\include{Chapters/design}

\chapter{Implementation}
\label{cha:implementation}

Where the design chapter concerned itself with the overall plan, this
is where the actual experiment in the form of an implementation is
taking form.  It is not the purpose of the implementation to fully
realise the design described in the previous chapter. It is the
exclusive purpose of the implementation (a subset of the design) to
either validate or refute the hypotheses put forth in the
introduction. This, and nothing else. If it does less, you have posed
questions you are not prepared to answer; if it does more, you should
be coding less or asking more questions.

If it illustrates core aspects, \eg, the inner working of a particular
important algorithm or function, code segments are welcome in this
chapter, as long as they are short, to the point, well-commented and
-formatted.  It is also a good idea to provide the reader with a
general overview of the structure of the code, as well as how
communication between various parts take place.  The complete code (as
well as your data) should be included separately with your report in
the form of a zip-file or USB-stick.

Overall, the implementation is the computer scientist's equivalent of
lab equipment carefully arranged into a experimental setup, and just
as the validity of an experimental investigation will be judged in
part on the craftsmanship of the setup, so will the quality of your
implementation. It is therefore important to clearly communicate how
your system works, so that the reader may have confidence in your
evaluation and conclusions.


\chapter{Evaluation}
\label{cha:evaluation}

Having built the equivalent of a experimental setup, it is time to use
the implementation to test the hypotheses.

This is usually broken down in stages and subquestions.

A structured approach to performing and reporting on experiments is
to follow this pattern for every single experiment:

\begin{enumerate}
\item What is the purpose of the experiment?
\item What is the expected outcome?
\item What are the parameters under which the experiment takes place?
\item What are the results?
\item How do the results align with the expected outcome? If they do
  not align, why is that so?
\end{enumerate}

Results should be presented summarised in tables and graphs.  Remember
to note the number of times experiments were repeated, as well as
averages, and standard deviations (in percent of the mean).  There is
much more to the proper evaluation of experimental data than can be
expounded upon here, but I turn the reader's attention to
\citep{Downey2011:TSPASFP2011}, which is freely available.


\chapter{Conclusion}
\label{cha:conclusion}

This, then is the grand summary of what you have accomplished.  You
may well imagine that many readers will read your Introduction, and
then skip to the Conclusion, and if, and only if, those two parts are
interesting, might be tempted to read the rest. A consequence is that
you should ensure that the reader will gain a good overall
understanding of what you have done by reading only the conclusion.
Thus, this is a place to summarise all that has gone before, before
finally concluding on the results of your experiments and the validity
of your hypotheses. It is also important to ensure that the
Introduction (which in all likelihood was written first) still aligns
closely with the conclusions reached.

If you so desire, this is also where you might add a section on Future
Work, where you point in the directions that should be followed to
complete the work you have already accomplished.



%\part{Some Kind of Manual}
%\include{Chapters/Chapter01}
%\cleardoublepage

%\part{The Showcase}
\include{Chapters/Chapter02}
%\addtocontents{toc}{\protect\clearpage} % <--- just debug stuff, ignore
\include{Chapters/Chapter03}



%\include{multiToC} % <--- just debug stuff, ignore for your documents
% ********************************************************************
% Backmatter
%*******************************************************
\appendix
%\renewcommand{\thechapter}{\alph{chapter}}
\cleardoublepage
\part{Appendix}
\include{Chapters/Chapter0A}
%********************************************************************
% Other Stuff in the Back
%*******************************************************
\cleardoublepage\include{FrontBackmatter/Bibliography}
\cleardoublepage\include{FrontBackmatter/Declaration}
\cleardoublepage\include{FrontBackmatter/Colophon}
% ********************************************************************
% Game Over: Restore, Restart, or Quit?
%*******************************************************
\end{document}
% ********************************************************************
